Does stomatal patterning in amphistomatous leaves minimize the CO\(_2\) diffusion path length within leaves?

### 2024-03-04 ms/ms.Rmd
updated funding information

  The authors thank two anonymous reviewers for feedback on an earlier version of this manuscript, NSF Award 1929167 to C.D.M., and NSF Award 2307341 to T.N.B. This is publication #218 from the School of Life Sciences, University of Hawaiʻi at Mānoa.

>>>>

  The authors thank two anonymous reviewers for feedback on an earlier version of this manuscript, NSF Award 1929167 to C.D.M., and USDA NIFA Hatch project 1016439 and NSF Award 2307341 to T.N.B. This is publication #218 from the School of Life Sciences, University of Hawaiʻi at Mānoa.

### 2024-03-04 ms/ms.tex
updated funding information

The authors thank two anonymous reviewers for feedback on an earlier
version of this manuscript, NSF Award 1929167 to C.D.M., and NSF Award
2307341 to T.N.B. This is publication \#218 from the School of Life
Sciences, University of Hawaiʻi at Mānoa.

>>>>

The authors thank two anonymous reviewers for feedback on an earlier
version of this manuscript, NSF Award 1929167 to C.D.M., and USDA NIFA
Hatch project 1016439 and NSF Award 2307341 to T.N.B. This is
publication \#218 from the School of Life Sciences, University of
Hawaiʻi at Mānoa.
